---
title: "TrajDataMining"
author: "Diego Monteiro"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TrajDataMining}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## TrajDataMining

The TrajDataMining contains a set of methods for trajectory data preparation, such as
filtering, compressing and clustering, and for trajectory pattern discovery. The meth-
ods for data preparation are important to prepare trajectory data sets before the data
mining phase. TrajDataMining contains the following methods:

- A speed filter that filters out trajectory observations whose speeds are above
a user-defined maximum velocity ( ETIENNE , 2011).

- Two compression algorithms: (1) Douglas-Peucker which reduces trajectories
by preserving spatial precisions ( DOUGLAS; PEUCKER , 1973), and (2) Open-window Meratnia-By which reduces trajectories by preserving spatiotempo-
ral precisions ( MERATNIA; BY , 2004).

- Two algorithms to discover when objects stop and move, CB-SMoT ( PALMA
et al. , 2008) and DB-SMoT ( ROCHA et al. , 2010), which can be used to semanti-
cally enrich the trajectory data.

- A method, named Partner, that identifies objects that are moving together.
We propose this method to recognize trajectories that stay together, based on
trajectory distance time series analysis.

## Example data gives
```{r}
library(TrajDataMining)
library(ggplot2)
library(grid)
library(rgdal)
```

## Plot of A1 data example

### A1 track its a trajectory of sea elephant

```{r ,fig.height=4,fig.width=4,fig.align='center'}

  df <- data.frame(x=A1@sp@coords[,1],y=A1@sp@coords[,2])

  ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("elephant sea Trajectory")+xlab("X")+ ylab("Y")+theme_classic()
  
```


## Douglas Peucker Method

### Method that reduces a trajectory spatially

```{r, fig.height=4,fig.width=4,fig.align='center'}

# get the maximum distance
 max <- max(A1@connections$distance)

 douglasp <- douglasPeucker(A1,max)
 
 df <- data.frame(x=douglasp@sp@coords[,1],y=douglasp@sp@coords[,2])
 ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("Method Douglas Peucker")+xlab("X")+ ylab("Y")+theme_classic()
 
```


## Speed Filter

### Method removes regions where speed was higher than the defined parameter

```{r, fig.height=4,fig.width=4,fig.align='center'}

# get the maximum distance
  sf <- speedFilter(A1,0.01)
  df <- data.frame(x=sf@sp@coords[,1],y=sf@sp@coords[,2])

   ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("Method Speed Filter")+xlab("X")+ ylab("Y")+theme_classic()
```

## ow Meratnia By Collection

### Method that reduces a set of trajectories spatiotemporally


```{r}

# plot(owMeratniaByCollection(tracksCollection,13804.84, 0.03182201))


```

## Partner

### Method to identify if two trajectories are partners

#### For to send this data for the database use the class DataSourceInfo.
```{r, fig.height=6,fig.width=6,fig.align='center'}
 
  data <- FALSE
  
  partner(A1,A2,110792,2277,0,data)

  

```






